A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
number
hah good job
Tolgonay fixes

\begin{table}
	\centering
	\begin{tabular}{lr}
		\toprule
		Part of speech & Number of stems\\
		\midrule
		Noun & 4,972\\
		Verb & 1,231 \\
		Adjective & 944\\
		Proper noun & 796\\
		Adverb & 295 \\
		Numeral & 63 \\
		Conjunction & 58 \\
		Postposition & 51 \\
		Pronoun & 29\\
		Determiner & 27\\
		\midrule
		Total: 8,466 & \\
		\bottomrule
	\end{tabular}
	\caption{Breakdown of number of stems in the lexicon by major part of speech. Minor categories, such as particle, modal and copula are left out.}\label{table:stems}
	%FIXME: are we putting captions above or below tables?  I like them better below, but I got the impression that there's some standard to have them above.  Maybe it was just UW being table Nazis for my MA thesis.
\end{table}

@@

\begin{table*}[htbp]
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known       & Naïve coverage (\%) & Mean ambiguity\\
		\midrule 
		Kyrgyz Wikipedia & 329,524   & 270,668     & 82.1 $\pm$ 3.2      & 2.35\\
		RFERL Kyrgyzstan & 4,112,558 & 3,614,193   & 87.9 $\pm$ 1.2      & \\
		\bottomrule
	\end{tabular}
	\caption{Naïve coverage and mean ambiguity of the analyser over two test corpora.}
	\label{table:cov}
\end{table*}

@@

We would like to thank: the Google Summer of Code 2011, which supported the development of the Turkish$\rightarrow$Kyrgyz MT system this transducer was designed for; Tolgonay Washington for native speaker intuitions of Kyrgyz and the anonymous reviewers for comments on how to improve the manuscript. This work has been partially funded by Spanish Ministerio de Ciencia e Innovación through project TIN2009-14009-C02-01.

>>>>

\begin{table}
	\centering
	\begin{tabular}{lr}
		\toprule
		Part of speech & Number of stems\\
		\midrule
		Noun & 4,972\\
		Verb & 1,231 \\
		Adjective & 944\\
		Proper noun & 796\\
		Adverb & 295 \\
		Numeral & 63 \\
		Conjunction & 58 \\
		Postposition & 51 \\
		Pronoun & 29\\
		Determiner & 27\\
		\midrule
		Total: & 8,466 \\
		\bottomrule
	\end{tabular}
	\caption{Breakdown of number of stems in the lexicon by major part of speech. Minor categories, such as particle, modal and copula are left out.}\label{table:stems}
	%FIXME: are we putting captions above or below tables?  I like them better below, but I got the impression that there's some standard to have them above.  Maybe it was just UW being table Nazis for my MA thesis.
\end{table}

@@

\begin{table*}[htbp]
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known       & Naïve coverage (\%) & Mean ambiguity\\
		\midrule 
		Kyrgyz Wikipedia & 329,524   & 270,668     & 82.1 $\pm$ 3.2      & 2.35\\
		RFERL Kyrgyzstan & 4,112,558 & 3,614,193   & 87.9 $\pm$ 1.2      & 2.43\\
		\bottomrule
	\end{tabular}
	\caption{Naïve coverage and mean ambiguity of the analyser over two test corpora.}
	\label{table:cov}
\end{table*}

@@

We would like to thank: the Google Summer of Code 2011, which supported the development of the Turkish$\rightarrow$Kyrgyz MT system this transducer was designed for; Tolgonay Kubatova for native speaker intuitions of Kyrgyz; and the anonymous reviewers for comments on how to improve the manuscript.  This work has been partially funded by Spanish Ministerio de Ciencia e Innovación through project TIN2009-14009-C02-01.
